External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-29 CVPR2017_Review_Unified.tex
add

We evaluate the performance of the proposed framework on denoising real noisy images. The denoising is simultaneously done with the guided internal dictionary learning (DL) process. We ignore the index $k\in\{1,...,K\}$ of subspace for notation simplicity. In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean subtracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction. Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in (\ref{equ9}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ. (\ref{equ10}). Then the $m$-th latent clean patch $\hat{\mathbf{y}}_{n,m}$ in the $n$-th PG $\mathbf{Y}_{n}$ is recovered by 
\vspace{-2mm}
\begin{equation}\label{equ12}\vspace{-2mm}
\hat{\mathbf{y}}_{n,m}=\mathbf{D}_{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
\end{equation}
where $n=1,...,N;m=1,...,M$.
\begin{table}
\label{alg1}
\begin{tabular}{l}
\hline
\textbf{Alg. 1}: External Patch Group (PG) Prior Guided Internal
\\
\quad \quad \quad PG Prior Learning for Image Denoising
\\
\hline
\textbf{Input:} Noisy image $\mathbf{y}$, external PG prior GMM model
\\
\textbf{Output:} The denoised image $\hat{\mathbf{x}}$.
\\
\textbf{Initialization:} $\hat{\mathbf{x}}^{(0)}=\mathbf{y}$;
\\
\textbf{for} $Ite = 1:IteNum$ \textbf{do}
\\
1. Extracting internal PGs from $\hat{\mathbf{x}}^{(Ite-1)}$;
\\
%\textbf{Guided Internal Subspace Selection:}
%\\
\quad\textbf{for} each PG $\mathbf{Y}_{n}$ \textbf{do}
\\
2.\quad Calculate group mean vector $\boldsymbol{\upmu}_{n}$ and form 
\\
\quad \ \ \ mean subtracted PG $\mathbf{\overline{Y}}_{n}$;
\\
3.\quad Subspace selection via Equ. (\ref{equ4});
\\
\quad\textbf{end for}
\\
%\textbf{Guided Internal Orthogonal Dictionary Learning:}
%\\
\quad\textbf{for} the PGs in each Subspace \textbf{do}
\\
4.\quad External PG prior Guided Internal Orthogonal
\\
\quad \ \ \ Dictionary Learning by solving (\ref{equ5});
\\
5.\quad Recover each patch in all PGs via Equ. (\ref{equ12});
\\
\quad\textbf{end for}
\\
6. Aggregate the recovered PGs of all subspaces to form
\\
\quad the recovered image $\hat{\mathbf{x}}^{(Ite)}$;
\\
\textbf{end for}
\\
\hline
\end{tabular}
\end{table}
The latent clean image $\hat{\mathbf{x}}$ is reconstructed by aggregating all the estimated PGs. Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs. The proposed denoising algorithm is summarized in Alg. 1.

@@

The comparisons are performed on two standard datasets in which the images were captured under indoor and outdoor lighting conditions by different types of cameras and camera settings. The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images. The noisy images were collected under controlled indoor environment. Some samples can be found in \cite{crosschannel2016}. For each image, the same scene was shot 500 times under the same camera and camera setting. The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed. Since the 17 images share repetitive contents, we cropped these images into 60 smaller images (of size $500\times 500\times3$) including different contents. Some samples are shown in Figure \ref{fig4}. We also perform comparison on the 15 testing images (of size $512\times 521\times3$) used in \cite{crosschannel2016}. Noted that the noise in the 15 images used in \cite{crosschannel2016} is different from the noise in the 60 images cropped from \cite{crosschannel2016} since they are taken in different shots. The second dataset provided in \cite{ncwebsite} includes about 20 real noisy images collected under uncontrolled outdoor environment. These images do not have "ground truth" images.

\begin{figure}[t]
\centering
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_73.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B2_80.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_21.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A4_51.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_6400_B3_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}
\end{minipage}
}
\caption{Some samples cropped from real noisy images of \cite{crosschannel2016}.}
\vspace{-4mm}
\label{fig4}
\end{figure}

@@

\subsection{Implementation Details}
Our proposed denoising method contains two stages, the external prior learning stage and the external prior guided internal learning stage. In the first stage, there are 4 parameters: the $p$ is set as $p = 6$ (hence the patch size is $6\times 6 \times 3$), the number of patches in a patch group (PG) is set as $M=10$, the window size for PG searching is set as $W=31$, and the number of Gaussians in Gaussian Mixture Model (GMM) is set as $K=32$. We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images. In the second stage, there are 4 parameters: the number of internal atoms in the learned dictionaries is set as $r=3p^2/2=54$, the sparse regularization parameter is set as $\lambda=0.001$, the number of iterations for solving problem (\ref{equ5}) is set as $T=2$, and the number of iterations for the denoising algorithm is set as $IteNum=4$. Our proposed method needs about 60 seconds to denoise an image of size $512\times512\times3$ under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.

\subsection{Comparison with External and Internal Priors}
In this section, we compare our proposed method on real image denoising with external prior based method (denoted as "External") and internal prior based method (denoted as "Internal"). All the three methods perform real image denoising under the weighted sparse coding framework in Equ. (\ref{equ5}). The "External" method employs the external dictionaries (i.e., $r=0$ in Equ. (\ref{equ5})) to recover the latent clean images, while the "Internal" method directly learn the subspace structures from the internal PGs via GMM and perform denoising with internal dictionary learning (i.e., $r=128$ in Equ. (\ref{equ5})). All parameters are tuned to achieve the best performance.

>>>>

We evaluate the performance of the proposed framework on denoising real noisy images. The denoising is simultaneously done with the guided internal dictionary learning (DL) process. We ignore the index $k\in\{1,...,K\}$ of subspace for notation simplicity. In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean subtracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction. Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in (\ref{equ9}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ. (\ref{equ10}). Then the $m$-th latent clean patch $\hat{\mathbf{y}}_{n,m}$ in the $n$-th PG $\mathbf{Y}_{n}$ is recovered by 
\vspace{-2mm}
\begin{equation}\label{equ12}\vspace{-2mm}
\hat{\mathbf{y}}_{n,m}=\mathbf{D}_{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
\end{equation}
where $n=1,...,N;m=1,...,M$.
\begin{table}\label{alg1}
\begin{tabular}{l}
\hline
\textbf{Alg. 1}: External Patch Group (PG) Prior Guided Internal
\\
\quad \quad \quad PG Prior Learning for Image Denoising
\\
\hline
\textbf{Input:} Noisy image $\mathbf{y}$, external PG prior GMM model
\\
\textbf{Output:} The denoised image $\hat{\mathbf{x}}$.
\\
\textbf{Initialization:} $\hat{\mathbf{x}}^{(0)}=\mathbf{y}$;
\\
\textbf{for} $Ite = 1:IteNum$ \textbf{do}
\\
1. Extracting internal PGs from $\hat{\mathbf{x}}^{(Ite-1)}$;
\\
%\textbf{Guided Internal Subspace Selection:}
%\\
\quad\textbf{for} each PG $\mathbf{Y}_{n}$ \textbf{do}
\\
2.\quad Calculate group mean vector $\boldsymbol{\upmu}_{n}$ and form 
\\
\quad \ \ \ mean subtracted PG $\mathbf{\overline{Y}}_{n}$;
\\
3.\quad Subspace selection via Equ. (\ref{equ4});
\\
\quad\textbf{end for}
\\
%\textbf{Guided Internal Orthogonal Dictionary Learning:}
%\\
\quad\textbf{for} the PGs in each Subspace \textbf{do}
\\
4.\quad External PG prior Guided Internal Orthogonal
\\
\quad \ \ \ Dictionary Learning by solving (\ref{equ5});
\\
5.\quad Recover each patch in all PGs via Equ. (\ref{equ12});
\\
\quad\textbf{end for}
\\
6. Aggregate the recovered PGs of all subspaces to form
\\
\quad the recovered image $\hat{\mathbf{x}}^{(Ite)}$;
\\
\textbf{end for}
\\
\hline
\end{tabular}
\end{table}
The latent clean image $\hat{\mathbf{x}}$ is reconstructed by aggregating all the estimated PGs. Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs. The proposed denoising algorithm is summarized in Alg. 1.

@@

The comparisons are performed on two standard datasets in which the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings. The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images. The noisy images were collected under controlled indoor environment. Some samples can be found in \cite{crosschannel2016}. For each image, the same scene was shot 500 times under the same camera and camera setting. The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed. Since the 17 images share repetitive contents, we cropped them into 60 smaller images (of size $500\times 500\times3$) including different contents. Some samples are shown in Figure \ref{fig4}. We also perform comparison on the 15 cropped images (of size $512\times 521\times3$) used in \cite{crosschannel2016}. Noted that the noise in the 15 images used in \cite{crosschannel2016} is different from the noise in the 60 images cropped from \cite{crosschannel2016} since they are taken in different shots. The second dataset provided in \cite{ncwebsite} includes about 20 real noisy images collected under uncontrolled outdoor environment. This dataset does not have "ground truth" images.

\begin{figure}[t]
\centering
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_73.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}
\end{minipage}
}\vspace{-3mm}
\subfigure{
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B2_80.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_21.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A4_51.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_6400_B3_95.png}
\end{minipage}
\begin{minipage}{0.055\textwidth}
\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}
\end{minipage}
}
\caption{Some samples cropped from real noisy images of \cite{crosschannel2016}.}
\vspace{-2mm}
\label{fig4}
\end{figure}

@@

\subsection{Implementation Details}
Our proposed method contains two stages, the external prior learning stage and the external prior guided internal learning stage. In the first stage, we set $p = 6$ (so the patch size is $6\times 6 \times 3$), $M=10$ (the number of patches in a patch group (PG)), $W=31$ (so the window size for PG searching is $31\times31$, and $K=32$ (the number of Gaussians in Gaussian Mixture Model (GMM)). We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images. In the second stage, we set $r=54$ (the number of internal atoms in the learned dictionaries), $\lambda=0.001$ (the sparse regularization parameter), $T=2$ (the number of iterations for solving problem (\ref{equ5})), and $IteNum=4$ (the number of iterations for Alg. 1). Our proposed method needs about 60 seconds to denoise an image of size $512\times512\times3$ under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.

\subsection{Comparison with External and Internal Priors}
In this section, we compare our proposed method on real image denoising with external prior based method (denoted as "External") and internal prior based method (denoted as "Internal"). All the three methods perform real image denoising under the weighted sparse coding framework in Equ. (\ref{equ5}). The "External" method employs the external dictionaries (i.e., $r=0$ in Equ. (\ref{equ5})) to recover the latent clean images, while the "Internal" method employ the GMM to directly cluster the internal noisy PGs into multiple subspaces, and perform denoising with internal dictionary learning (i.e., $r=128$ in Equ. (\ref{equ5})) for each subspace. All parameters of the three methods are tuned to achieve corresponding best performance.
